Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-02 ms/main.tex
typo

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :

>>>>

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
